---
title: "analysis3_ML"
author: "Ehsan"
date: "11/5/2021"
output: html_document
---

```{r}
library(skimr)
library(dplyr) #for data processing
library(here)
library(rsample)
library(recipes)
library(tidymodels)
library(table1)
library(rpart)
library(vip)
```

#locating the data
```{r}
data_location <-here::here("data","processed_data","processeddata.rds")
data <- readRDS(data_location)
```
#have a look at the data
```{r}
glimpse(data)
```

#Part 1: Preprocessing
#Preprocessing: Feature removal. Removing coughYN, coughYN2 and myalgiaYn columns.
```{r}
data_1 <-  select(data, -c(CoughYN, WeaknessYN, CoughYN2, MyalgiaYN))
```
#checking of the number of columns actually got reduced or not
```{r}
glimpse(data_1)
```
#ordering factors for Weakness, CoughIntensity, Myalgia 
```{r}
data_2 <- mutate(data_1, Weakness = factor(Weakness, levels = c("None", "Mild","Moderate","Severe"),ordered = TRUE))
data_3 <- mutate(data_2, CoughIntensity = factor(CoughIntensity, levels = c("None", "Mild", "Moderate","Severe"),ordered = TRUE))
data_4 <- mutate(data_3, Myalgia = factor(Myalgia, levels = c("None", "Mild", "Moderate","Severe"),ordered = TRUE))
```
#checking if those three coumn are actually ordered or not.
```{r}
skim(data_4)
```
#Finding out which categories have less than 50 inputs
```{r}
table <- table1(~ . , data=data_4, overall="Total")
table
```
#dropping the two column that have <50 inputs
```{r}
ML_processed<- data_4%>%
  select(-c(Hearing, Vision))
```
#checking if it was removed successfully
```{r}
glimpse(ML_processed)
```

#Part2: Analysis
#set random seed to 123
```{r}
set.seed(123)
```
# Put 70% of the data into the training set and 30% into testing using strata=BodyTemp
```{r}
data_split <- initial_split(ML_processed, prop = 0.7, strata = BodyTemp)
```
# Create data frames for the two sets:
```{r}
train_data <- training(data_split)
test_data  <- testing(data_split)
```

# training set proportions by class
```{r}
train_data %>% 
  count(BodyTemp) %>% 
  mutate(prop = n/sum(n))
```
# test set proportions by class
```{r}
test_data %>% 
  count(BodyTemp) %>% 
  mutate(prop = n/sum(n))
```
##5-fold cross validation, 5 times repeated, stratified on `BodyTemp` for the CV folds
```{r}
folds <- vfold_cv(train_data, v = 5, repeats =5, strata= "BodyTemp")
```
#create recipe that codes categorical variables as dummy variables
```{r}
flu_recipe <- recipe(BodyTemp ~ ., data = train_data) %>%
           step_dummy(all_nominal_predictors())
```

#Build a null model
```{r}
null_mod <- linear_reg() %>%
  set_engine("lm") 
```
#Model workflow pairs a model and recipe together
```{r}
null_workflow <- 
  workflow() %>%
  add_model(null_mod) %>%
  add_recipe(flu_recipe)
```
#"fit" model to training data
```{r}
null_train <- null_workflow %>%
                fit(data = train_data)
```
# Obtaining Predictions
```{r}
predict(null_train, train_data) #make prediction
null_augment_train <- augment(null_train, train_data) #use augment
null_augment_train %>% select(BodyTemp)
```
# Calculating Root RMSE 
```{r}
rmse_train <- null_augment_train %>% rmse(truth = BodyTemp, .pred) #calculate rmse
rmse_train
```


#"fit" model to test data
```{r}
null_test <- null_workflow %>%
                fit(data = test_data)
```
# Obtaining Predictions
```{r}
predict(null_test, test_data) #make prediction
null_augment_test <- augment(null_test, test_data) #use augment
null_augment_test %>% select(BodyTemp)
```
# Calculating Root RMSE 
```{r}
rmse_test <- null_augment_test %>% rmse(truth = BodyTemp, .pred) #calculate rmse
rmse_test
```


#part 3: We'll use three models

#3.1: Tree model
#define the tree model [code from https://www.tidymodels.org/start/tuning/]
```{r}
tune_spec <-
  decision_tree(
    cost_complexity = tune(),
    tree_depth = tune(),
  ) %>%
  set_engine("rpart") %>%
  set_mode("regression") ##'regression' instead of 'classification'
tune_spec
```

# tuning grid specification
```{r}
tree_grid <- grid_regular(cost_complexity(),
                          tree_depth(),
                          levels = 5)
```
#define workflow for tree
```{r}
tree_workflow <- workflow() %>%
               add_model(tune_spec) %>%
               add_recipe(flu_recipe) #recipe from line 95
```

```{r}
# tuning using cross-validation and the tune_grid() function
tree_res <- 
  tree_workflow %>% 
  tune_grid(resamples = folds, grid = tree_grid)
```

```{r}
tree_res %>% 
  collect_metrics()
```

#plotting metrics
```{r}
tree_res %>%
  collect_metrics() %>%
  mutate(tree_depth = factor(tree_depth)) %>%
  ggplot(aes(cost_complexity, mean, color = tree_depth)) +
  geom_line(size = 1.5, alpha = 0.6) +
  geom_point(size = 2) +
  facet_wrap(~ .metric, scales = "free", nrow = 2) +
  scale_x_log10(labels = scales::label_number()) +
  scale_color_viridis_d(option = "plasma", begin = .9, end = 0)
```
#finding best model               
```{r}
tree_res %>%
  show_best("rmse")
```
#continued
```{r}
best_tree <- tree_res %>%
  select_best("rmse")
best_tree
```
#finalize workflow
```{r}
final_wf <- 
  tree_workflow %>% 
  finalize_workflow(best_tree)
final_wf
```
# final workflow using the fit() function
```{r}
final_fit <- 
  final_wf %>%
  last_fit(data_split) 
```

```{r}
final_fit %>%
  collect_metrics() 
```
#predictions
```{r}
tree_prediction <- final_fit %>%
  collect_predictions() 
```

# Make two plots, model predictions from the tuned model versus actual outcomes
  
```{r}
ggplot(data=tree_prediction, aes(x=.pred, y=BodyTemp)) + geom_point() + labs(title= "Plot of Model Predictions from Tuned Model vs Actual Outcomes", 
       x= "Model Predictions", y= "Actual Outcomes") 
```
#calculating residuals
```{r}
tree_prediction$resid <- tree_prediction$BodyTemp - tree_prediction$.pred 
```
# plotting residuals 
```{r}
ggplot(data=tree_prediction, aes(x=.pred , y=resid)) + geom_point() +
  labs(title= "Plot of Model Predictions from Tuned Model vs Actual Outcomes", 
       x= "Model Predictions", y= "Residuals") 
```

```{r}
show_best(final_fit, metric= "rmse")
```

# Estimate variable importance based on the model’s structure.
```{r}
library(vip)
final_fit %>% 
  extract_fit_parsnip() %>% 
  vip()
```