---
title: "analysisscript2"
author: "Ehsan"
date: "10/20/2021"
output: html_document
---
# Libraries 
```{r}
library(tidyverse)
library(tidymodels)
library(dplyr)
library(here)
```

#Load data
```{r}
data_location <- here::here("data","processed_data","processeddata.rds")
```
```{r}
data <- readRDS(data_location)
```
#set seed for random numbers
```{r}
set.seed(222)
```
#put 3/4 of data into the training set
```{r}
split_data <- initial_split(data, prop = 3/4)
```
# create two dataframe: test and training
```{r}
training_data <- training(split_data)
test_data  <- testing(split_data)
```
#Create a simple recipe that fits categorical outcome of interest (Nausea) to all predictors.
```{r}
nausea_recipe <- recipe(Nausea ~., data = training_data)
```
#path for logistic regression model
```{r}
lg_mod <- logistic_reg() %>% 
  set_engine("glm")
```
#create workflow, add model type and the recipe 
```{r}
Nausea_workflow <- 
  workflow() %>% 
  add_model(lg_mod) %>% 
  add_recipe(nausea_recipe) 
```
#model fitting to training data 
```{r}
Nausea_fit <- 
  Nausea_workflow %>% 
  fit(data = training_data)
```
#how it looks
```{r}
Nausea_fit %>% 
  extract_fit_parsnip() %>% 
  tidy()
```
#applying oit to make some predictions on test data
```{r}
predict(Nausea_fit, test_data)
```
#more prediction using augment. 
```{r}
Nausea_augment_predict <- 
  augment(Nausea_fit, test_data)
```
#evaluate ROC and ROC_auc to see how good it fits the data
```{r}
Nausea_augment_predict %>% 
  roc_curve(truth = Nausea, .pred_Yes, event_level = "second") %>% 
  autoplot()
```
 
```{r}
Nausea_augment_predict %>%
  roc_auc(truth = Nausea, .pred_Yes, event_level = "second")
```
#roc_auc value is 0.72, which is good.

#predict, augment, ROC-curve, roc_auc for the training data this time
```{r}
predict(Nausea_fit, training_data)
```

```{r}
Nausea_augment_predict1 <- 
  augment(Nausea_fit, training_data)
```

```{r}
Nausea_augment_predict1 %>% 
  roc_curve(truth = Nausea, .pred_Yes, event_level = "second") %>% 
  autoplot()
```
  
```{r}
Nausea_augment_predict1 %>%
  roc_auc(truth = Nausea, .pred_Yes, event_level = "second")
```
#roc_auc value is 0.78, which is good.



#Alternative model using just the main predictor: runny nose. Making recipe
```{r}
nausea_rec_Alt <- recipes::recipe(Nausea ~ RunnyNose, data = training_data)
```

```{r}
lg_mod <- logistic_reg() %>% 
  set_engine("glm")
```
#creating workflow with the alternative recipe
```{r}
Nausea_Alt_workflow <- 
  workflow() %>% 
  add_model(lg_mod) %>% 
  add_recipe(nausea_rec_Alt) 
```
#fit it to training data
```{r}
Nausea_fit2 <- 
  Nausea_Alt_workflow %>% 
  fit(data = training_data)
```
#see how it looks
```{r}
Nausea_fit2 %>% 
  extract_fit_parsnip() %>% 
  tidy()
```
#prediction from test data
```{r}
predict(Nausea_fit2, test_data)
```

#prediction + augment from test data
```{r}
Nausea_augment_predict3 <- 
  augment(Nausea_fit2, test_data)
```
#roc_curve and roc_auc from test data
```{r}
Nausea_augment_predict3 %>% 
  roc_curve(truth = Nausea, .pred_Yes, event_level = "second") %>% 
  autoplot()
```
  
```{r}
Nausea_augment_predict3 %>%
  roc_auc(truth = Nausea, .pred_Yes, event_level = "second")
```
#now predict, predict+augment, roc_curve and roc_Auc for the test data
```{r}
predict(Nausea_fit2, training_data)
```

```{r}
Nausea_augment_predict4 <- 
  augment(Nausea_fit2, training_data)
```

```{r}
Nausea_augment_predict4 %>% 
  roc_curve(truth = Nausea, .pred_Yes, event_level = "second") %>% 
  autoplot()
```
  
```{r}
Nausea_augment_predict4 %>%
  roc_auc(truth = Nausea, .pred_Yes, event_level = "second")
```
#roc-auc value for both test and training data set using the alternative model is below 0.5. So this alternative model is not a good fit.
